Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
finetuning

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is the tensor product of the unit map $1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

@@

We have implemented the first step in the proof strategy.
This section is devoted to the remaining steps.
First, we explain steps (2)-(4), which are rather formal.
Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
Finally, we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\]
where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
\owen{Calibrate notations!}
It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.

@@

\owen{Below is Greg's summary of the proof.}

Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
is that we only have to prove the factorization algebra part of the main theorem. 
To do so, we first use the universal property of the centralizer to obtain 
a canonical factorization algebra map 
\[\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\]
where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).

Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
this map is a weak-equivalence.

@@

\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.}

To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
we can associate its Chevalley-Eilenberg cochain complex defined 
by 
\begin{equation}
 \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
\end{equation}
with its classical differential. 
\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
We have the evaluation map 
\begin{equation}
 \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
\end{equation}
given by applying a function on a given tensor in $Sym(\fg[-1])$.

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\Theta_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\Theta_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

\begin{lmm}
The assignment
\[
V \mapsto \Theta_{\bf{f}}(V)
\]
determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

\begin{lmm}
\label{L:pairingCE}
The natural transformation $\Theta_{\bf{f}}$ determines a map of strict prefactorization algebras,
i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
\end{lmm}

\subsection{}

We write, $1$ for the factorization algebra map defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras.

\begin{lmm}\label{L:ComTriangCent} The triangle 
 $$ \xymatrix{
& \clies ( \fg\otimes \Omega^* , B) \otimes \cliels(\fg\otimes \Omega^*_c   )
\ar[dr]^{\ev_f} & \\
\cliels(\fg\otimes \Omega^*_c ) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B.}
 $$
is a commutative triangle of factorization algebras maps.
\end{lmm}
\begin{proof}
 It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras. Since the unit $\mathbf{1}:Sym(\fg \otimes \Omega(U)[1]) \to B(U)$ is induced, for all $U$, by the factorization structure from the empty set $\emptyset$, we obtain that its support $I_{\mathbf{1}}=\emptyset$. 
 Therefore, formula~\eqref{eq:defineevJ} yields that 
 \[\ev_{f} (\mathbf{1}\otimes X) = \ev_{\emptyset}(\tilde{\mathbf{1}}\otimes X) 
 = \mathbf{f}(X)\] which proves the commutativity.
\end{proof}

By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big) 
 \longrightarrow B$ induces 
a canonical morphism of factorization algebras
\begin{equation}\label{eq:canonicaltocenter}
\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f}). 
\end{equation}

\subsection{The map $\theta_f$ is a weak equivalence.} 
We have defined a functorial (in $f$) factorization algebras map 
$\theta_f$.

>>>>

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $\id: A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\]
where ${\frak Z}(\mathbf{f})$ is a factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
\owen{Calibrate notations!}
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

@@

@@

\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.
It can just be a compendium of facts we use below.}

To any $\fg$-module $M$ (whether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
we can associate its Chevalley-Eilenberg cochain complex defined 
by 
\begin{equation}
 \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
\end{equation}
with its classical differential. 
\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
We have the evaluation map 
\begin{equation}
 \label{eq:defev} \ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
\end{equation}
given by applying a function on a given tensor in $Sym(\fg[-1])$.

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\ev_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\ev_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

\begin{lmm}
The assignment
\[
V \mapsto \ev_{\bf{f}}(V)
\]
determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

\begin{lmm}
\label{L:pairingCE}
The natural transformation $\ev_{\bf{f}}$ determines a map of strict prefactorization algebras,
i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
\end{lmm}

\subsection{The pairing fits into a centralizer diagram}

For any factorization algebra $B$ on $\RR^n$, 
there is a unit map of factorization algebras  
\[
1(U) = k \cong 1(\emptyset)  \xto{\cong}
B(\emptyset) \to B(V)  
\] 
for each open set $V$, where the last map is structure map of~$B$.

\begin{lmm}\label{L:ComTriangCent} 
There is a commutative triangle 
\[
\xymatrix{
& \clies ( \Omega \otimes \fg , (\bU_n \fh)_f) \otimes \bU_n \fg
\ar[dr]^{\ev_{\bf{f}}} & \\
\bU_n \fg \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  \bU_n \fh}
\]
of maps of factorization algebras.
\end{lmm}

\begin{proof}
This triangle commutes on the nose, as we now show.
What we need to show is how the unit map $u$ for $\clies ( \Omega \otimes \fg , (\bU_n \fh)_f)$ encodes the map $\bf{f}$.
\owen{I'm stuck. Greg's statement is below.}
 It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras. Since the unit $\mathbf{1}:Sym(\fg \otimes \Omega(U)[1]) \to B(U)$ is induced, for all $U$, by the factorization structure from the empty set $\emptyset$, we obtain that its support $I_{\mathbf{1}}=\emptyset$. 
 Therefore, formula~\eqref{eq:defineevJ} yields that 
 \[\ev_{f} (\mathbf{1}\otimes X) = \ev_{\emptyset}(\tilde{\mathbf{1}}\otimes X) 
 = \mathbf{f}(X)\] which proves the commutativity.
\end{proof}

By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_{\bf{f}}$ induces a canonical morphism 
\begin{equation}
\label{eq:canonicaltocenter}
\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\end{equation}
of factorization algebras.

\subsection{The map $\theta_{\bf{f}}$ is a weak equivalence.}

We have defined a functorial (in $f$) factorization algebras map 
$\theta_f$.
